DDS4Chl: A dataset of drought indices of water demand and supply and its impact on vegetation for continental Chile

### 2024-01-05 conference/IGARSS2024.qmd
first version of the article igarss2023

```{r}
#| fig-pos: "!ht"
#| fig-cap: "Linear trend of the SPI at time scales of 1, 3, 6, 12, 24, and 36 months for 1981-2023"
knitr::include_graphics("../output/figs/trend_raster_SPI_1981-2023.png")
```

>>>>

For the SPI, in the macrozones "norte chico", "central", and "sur" the trend decrease with the time scales of the index. Showing that at longer scales (e.g, 36 months) it reaches a trend of -0.056 (z-score) per decade (@fig-trendSPI). In the case of the AED measured by the EDDI. It shows a positive trend, caused by a increase on AED. The trend on EDDI reaches 0.053 per decade from the macrozones "norte grande" and "norte chico".

```{r fig-trendSPI}
#| fig-pos: "!ht"
#| fig-cap: "Linear trend of the SPI at time scales of 1, 3, 6, 12, 24, and 36 months for 1981-2023"
knitr::include_graphics("../output/figs/trend_raster_SPI_1981-2023.png")
```
